### 2011-02-10 doc/MVSeg.tex
ENH: updating atropos and MVSeg doc

\subsection{A quick tensor segmentation example}
atropos seg example with dti

two questions --- one of representation , one of distance.  that is,
distances on what?
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6in]{Figures/macaque_rgb.pdf}
\end{tabular}
\caption{We perform an RGB-based segmentation of the macaque
  population average tensor image.  At left is the manually placed
  labels, as performed in ITK-Snap.  At right is the Atropos result.
  You may repeat this study by labeling the macaque image with labels
  1, 2 and 3 (R, G, B) similarly to this example.  You then
  save the segmentation and run the script entitled MVSeg/src/scripts/seg\_dti\_manual\_init\_atropos.}
\label{fig:example1}
\end{center}
\end{figure}

>>>>

So, we have two questions---one of representation , one of distance.  That is,
what distances should we apply to what represenation of DTI data?

\subsection{A quick tensor segmentation example}
Figure~\ref{fig:macaque} shows a population average of DTI data for
the macaque monkey.  We segment the image by manually seeding each of
3 classes (R, G and B) by hand and then calling the Atropos
algorithm.  This parcellates the white matter within the automatically
generated mask into regions where the tract directionality is
primarily left-right (red), anterior-posterior (green) and
inferior-superior (blue).  While this is somewhat anatomically
meaningful, we would like to improve upon these results.  See, for
instance, Figure~\ref{fig:example1} which parcellates the brain into
anatomically determined regions.  
\begin{figure}
\begin{center}
\begin{tabular}{c}
\includegraphics[width=6in]{Figures/macaque_rgb.pdf}
\end{tabular}
\caption{We perform an RGB-based segmentation of the macaque
  population average tensor image.  At left is the manually placed
  labels, as performed in ITK-Snap.  At right is the Atropos result.
  You may repeat this study by labeling the macaque image with labels
  1, 2 and 3 (R, G, B) similarly to this example.  You then
  save the segmentation and run the script entitled MVSeg/src/scripts/seg\_dti\_manual\_init\_atropos.}
\label{fig:macaque}
\end{center}
\end{figure}
